---
title: "BC DxH/Sysmex XN IRF Correlation"
author: "Amrom"
date: "2018-08-31"
output: workflowr::wflow_html
---

## Introduction


At Children's Hospital of Philadelphia we assessed approximately 150 specimens. 

Analyzers
- BC DxH
- Sysmex XN

Unfortunately we could not perform testing in triplicate.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
libloc<-"~/icsh_irf/library"
library(knitr)
opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
library(purrr,lib.loc=libloc)
library(tidyr,lib.loc=libloc)
library(stringr,lib.loc=libloc)
library(ggplot2,lib.loc=libloc)
library(dplyr,lib.loc=libloc)
library(here,lib.loc=libloc)
library(janitor,lib.loc=libloc)
library(mcr,lib.loc=libloc)
library(readxl,lib.loc=libloc)
library(cowplot,lib.loc=libloc)



```


```{r}
load(here("prepped_data","hup.Rdata"))
load(here("prepped_data","chop.Rdata"))

```

```{r}
matchup<-read_xlsx(here("data","sample matchup.xlsx"))
```

## Data

```{r}
matchup <- matchup %>% 
  mutate(date = format(date, "%m-%d-%Y")) %>% 
  mutate(chop_id = paste0(date,"__",sys_id))

chop <- chop %>% 
  mutate(chop_id = paste0(date,"__",sample_no)) %>% 
  mutate(chop_id = str_replace_all(chop_id,"/","-"))

colnames(chop)[3:5] <- paste0(colnames(chop)[3:5],"_chop")
colnames(hup)[3:5] <- paste0(colnames(hup)[3:5],"_hup")

df<-matchup %>% 
  left_join(chop, by="chop_id") %>% 
  left_join(hup,by=c("dxh_id" = "Sample")) %>% 
  mutate(IRF_hup = 100*IRF_hup)

df %>% 
  select(date.x,starts_with("ret"),starts_with("irf")) %>% 
  DT::datatable(colnames = c("Date","RET% XN","RET XN","RET% DxH","RET DxH","IRF XN","IRF DxH"))
```


## Plots

Data was visualized with dot plots overlayed with loess smooth curves. Plot A below demonstrates a non-linear relationship between results from the two analyzers. Logarithmic transformation of the XN IRF results yielded a more linear relationship. As a result Passing Bablok regression was pursued using log transformed XN data.


```{r}

p1<-ggplot(df,aes(irf_percent_chop,IRF_hup))+
  geom_point()+
  geom_smooth()+
  labs(x="IRF Sysmex XN",y="IRF BC DxH")


p2<-ggplot(df,aes(irf_percent_chop,IRF_hup))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()+
  labs(x="IRF Sysmex XN (log axis)",y="IRF BC DxH")



myp<-plot_grid(p1,p2,labels = "AUTO")
myp2<-add_sub(myp, "A. Plot represents correlation of IRF between DxH and XN.\nB. Correlation plotting XN data on log scale", x = 0, hjust = 0)
ggdraw(myp2)
  
```

Bias Plots
```{r}
df<-df %>% 
  rowwise() %>% 
  mutate(avg = sum(IRF_hup,irf_percent_chop)/2,
         delta = IRF_hup - irf_percent_chop,
         delta_p = delta/avg)

avg_delta<-mean(df$delta,na.rm = T)
avg_delta_p<-mean(df$delta_p,na.rm = T)

ggplot(df,aes(avg,delta))+
  geom_point()+
  geom_hline(yintercept = avg_delta)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="DxH - XN")

ggplot(df,aes(avg,delta_p))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="Percent difference")
  
```



## Passing Bablok regression

A Passing Bablok regression model was fitted using the log transformed XN IRF data and the raw DxH data. 

```{r, results='markup', include=FALSE}

pbreg<-mcreg(log10(df$irf_percent_chop),(df$IRF_hup), method.reg = "PaBa",na.rm = TRUE)

b0<-pbreg@glob.coef[1] %>% round(3)
b1<-pbreg@glob.coef[2] %>% round(3)
estim<- pbreg@para

LCI.I<-estim[1,3] %>% round(3)
UCI.I<-estim[1,4] %>% round(3)
LCI.S<-estim[2,3] %>% round(3)
UCI.S<-estim[2,4] %>% round(3)

pcro<-cor(log10(df$irf_percent_chop),(df$IRF_hup),use = "complete.obs",method = "pearson") %>% round(3)


```

Results demonstrate a pearson correlation coefficient of `r pcro`. Slope estimate was `r b1` (95% CI `r UCI.S`-`r LCI.S`) and intercept was `r b0` (95% CI `r UCI.I`-`r LCI.I`). The model is plotted below.

```{r}
plot(pbreg,  x.lab = "Log Sysmex XN", y.lab = "BC DxH")

# sctest(log10(df$irf_percent_chop)~df$IRF_hup)

```

Using the model to generate an "adjusted" IRF for the XN, below would be the correlation plot and the bias plots.

```{r}
df<-df %>% 
  mutate(d_irf = log10(irf_percent_chop)*b1+b0) %>% 
  rowwise() %>% 
  mutate(avg_d = sum(IRF_hup,d_irf)/2,
         delta_d = IRF_hup - d_irf,
         delta_p_d = delta_d/IRF_hup)

avg_delta_d<-mean(df$delta_d,na.rm = T)
avg_delta_p_d<-mean(df$delta_p_d,na.rm = T)

ggplot(df,aes(d_irf,IRF_hup))+
  geom_point()+
  geom_smooth(method = 'lm')+
  labs(x="Adjusted IRF Sysmex XN",y="IRF BC DxH")
```

```{r}
p1<-ggplot(df,aes(d_irf,delta_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="DxH - XN")

p2<-ggplot(df,aes(d_irf,delta_p_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Percent difference")

plot_grid(p1,p2)

  
```

```{r}
qqnorm(df$delta_d)
```

```{r}
df <- df %>% 
  rowwise() %>% 
  mutate(oldcv = sd(c(irf_percent_chop,IRF_hup),na.rm = TRUE)/mean(c(irf_percent_chop,IRF_hup))) %>% 
  mutate(newcv = sd(c(irf_percent_chop,IRF_hup),na.rm = TRUE)/mean(c(d_irf,IRF_hup))) %>% 
  ungroup

cv_pvalue <- t.test(df$oldcv,df$newcv,var.equal = TRUE)$p.value 
  
cv_result<-df %>% summarise(oldcv_mean=mean(oldcv, na.rm = TRUE),
            newcv_mean=mean(newcv, na.rm = TRUE))
  

```

## Simulated Harmonization

We next calculated the the coefficient of variation between measures of IRF from the instruments and after simulated harmonization. Simulated harmonization means using the results of the Passing-Bablok regression to predict how a calibration procedure would alter the results. These simultated results are then used to calculate a predicted coefficient of variation after a calibration procedure.

Using the original IRF data, the CV between the methods is `r cv_result$oldcv_mean`. After adjust the data using the regression equation, the CV reduces to `r cv_result$newcv_mean`. This result is statistically significant (P=`cv_pvalue`)

