---
title: "Mindray 860/Sysmex XN IRF Correlation"
author: "Amrom"
date: "2018-09-06"
output: workflowr::wflow_html
---

## Introduction


At xx assessed approximately xxx specimens. 

Analyzers
- 
- 



```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("~/icsh_irf/functions/funs.R")
load_libs()
```


```{r}
mydata<-read_xlsx(here("data","spain.xlsx"),sheet = 2,range = "A2:I372")
```

## Data

```{r}
colnames(mydata)<-mydata %>%
  clean_names() %>% 
  colnames() %>% 
  paste0("_XX") %>% 
  str_replace_all(pattern = "1_XX","mind") %>% 
  str_replace_all(pattern = "XX","xn")


```


```{r}

mydata <- mydata %>% 
  tidyr::fill(x_mind,.direction="down") %>% 
  filter(!str_detect(irf_xn,"nalyz")) %>% 
  mutate_at(2:9,as.numeric) 

```


```{r}
mydf <- mydata %>% 
  group_by(x_mind) %>% 
  summarise_all(mean)
```


```{r}
gg<- mydf %>% 
  gather(key = "param",value = "value",-x_mind)
ggplot(gg,aes(value))+
  geom_histogram()+
  facet_wrap(~param,scales = "free")
```

## Plots

Data was visualized with dot plots overlayed with loess smooth curve (blue) and a linear model. Since the linear model approximated the data well, a Deming regression was pursued on untransformed data.


```{r}

ggplot(mydf,aes(irf_xn,irf_mind))+
  geom_point()+
  geom_smooth()+
  geom_smooth(method = "lm",se=FALSE,color="green")+
  labs(x="IRF Sysmex XN",y="IRF Mindray")

cor(mydf$irf_xn,mydf$irf_mind)

```


Bias Plots
```{r}

biaser<-function(x,y){

df<-data_frame(x,y)  
colnames(df)<-c("x","y")
df<-df %>% 
  rowwise() %>% 
  mutate(avg = sum(x,y)/2,
         delta = x - y,
         delta_p = delta/avg)

avg_delta<-mean(df$delta,na.rm = T)
avg_delta_p<-mean(df$delta_p,na.rm = T)

p1<-ggplot(df,aes(avg,delta))+
  geom_point()+
  geom_hline(yintercept = avg_delta)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Average IRF",
       y="DxH - XN")

p2<-ggplot(df,aes(avg,delta_p))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Average IRF",
       y="Percent difference")
list(p1,p2)

}  

xx<-biaser(mydf$irf_xn,mydf$irf_mind)
xx[[1]]<-xx[[1]]+labs(y="XN - Mindray")

plot_grid(xx[[1]],xx[[2]])

```



## Deming regression

A Deming regression model was fitted using the log transformed XN IRF data and the raw DxH data. 

```{r, results='markup', include=FALSE}

mydems<- function(x,y) {

pbreg<-mcreg(x,y, method.reg = "PaBa",na.rm = TRUE)

b0<-pbreg@glob.coef[1] %>% round(3)
b1<-pbreg@glob.coef[2] %>% round(3)
estim<- pbreg@para

LCI.I<-estim[1,3] %>% round(3)
UCI.I<-estim[1,4] %>% round(3)
LCI.S<-estim[2,3] %>% round(3)
UCI.S<-estim[2,4] %>% round(3)

pcro<-cor(x,y,use = "complete.obs",method = "pearson") %>% round(3)

list(pbreg,b0,b1,LCI.I,UCI.I,LCI.S,UCI.S,pcro)
}

dems<-mydems(mydf$irf_xn,mydf$irf_mind)

plot(dems[[1]],  x.lab = "Sysmex XN", y.lab = "Mindray")

```


Using the model to generate an "adjusted" IRF for the XN, below would be the correlation plot and the bias plots.

```{r}
df<-mydf %>% 
  mutate(d_irf =  irf_xn * dems[[3]] + dems[[2]]) %>% 
  rowwise() %>% 
  mutate(avg_d = sum(irf_mind,d_irf)/2,
         delta_d = irf_mind - d_irf,
         delta_p_d = delta_d/irf_mind)

avg_delta_d<-mean(df$delta_d,na.rm = T)
avg_delta_p_d<-mean(df$delta_p_d,na.rm = T)

ggplot(df,aes(d_irf,irf_mind))+
  geom_point()+
  geom_smooth()+
  labs(x="Adjusted IRF Sysmex XN",y="IRF BC DxH")
```

```{r}
ggplot(df,aes(avg_d,delta_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Mindray - XN")

ggplot(df,aes(avg_d,delta_p_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Percent difference")
  
```

```{r}
#qqnorm(df$delta_d)
```

