---
title: "Mindray 860/Sysmex XN IRF Correlation"
author: "Amrom"
date: "2018-09-06"
output: workflowr::wflow_html
---

## Introduction


At xx assessed approximately xxx specimens. 

Analyzers
- 
- 



```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("~/icsh_irf/functions/funs.R")
load_libs()
```


```{r}
mydata<-read_xlsx(here("data","spain.xlsx"),sheet = 2,range = "A2:I372")
```

## Data

```{r}
colnames(mydata)<-mydata %>%
  clean_names() %>% 
  colnames() %>% 
  paste0("_XX") %>% 
  str_replace_all(pattern = "1_XX","mind") %>% 
  str_replace_all(pattern = "XX","xn")


```


```{r}

mydata <- mydata %>% 
  tidyr::fill(x_mind,.direction="down") %>% 
  filter(!str_detect(irf_xn,"nalyz")) %>% 
  mutate_at(2:9,as.numeric) 

```


```{r}
mydf <- mydata %>% 
  group_by(x_mind) %>% 
  summarise_all(mean)
```


```{r}
gg<- mydf %>% 
  gather(key = "param",value = "value",-x_mind)
ggplot(gg,aes(value))+
  geom_histogram()+
  facet_wrap(~param,scales = "free")
```

## Plots

Data was visualized with dot plots overlayed with loess smooth curves. Plot A below demonstrates a non-linear relationship between results from the two analyzers. Logarithmic transformation of the XN IRF results yielded a more linear relationship. As a result Deming regression was pursued using log transformed XN data.


```{r, eval=FALSE}

p1<-ggplot(df,aes(irf_percent_chop,IRF_hup))+
  geom_point()+
  geom_smooth()+
  labs(x="IRF Sysmex XN",y="IRF BC DxH")


p2<-ggplot(df,aes(irf_percent_chop,IRF_hup))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()+
  labs(x="IRF Sysmex XN (log axis)",y="IRF BC DxH")



myp<-plot_grid(p1,p2,labels = "AUTO")
myp2<-add_sub(myp, "A. Plot represents correlation of IRF between DxH and XN.\nB. Correlation plotting XN data on log scale", x = 0, hjust = 0)
ggdraw(myp2)
  
```

Bias Plots
```{r, eval=FALSE}
df<-df %>% 
  rowwise() %>% 
  mutate(avg = sum(IRF_hup,irf_percent_chop)/2,
         delta = IRF_hup - irf_percent_chop,
         delta_p = delta/avg)

avg_delta<-mean(df$delta,na.rm = T)
avg_delta_p<-mean(df$delta_p,na.rm = T)

ggplot(df,aes(avg,delta))+
  geom_point()+
  geom_hline(yintercept = avg_delta)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="DxH - XN")

ggplot(df,aes(avg,delta_p))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="Percent difference")
  
```



## Deming regression

A Deming regression model was fitted using the log transformed XN IRF data and the raw DxH data. 

```{r, results='markup', include=FALSE, eval=FALSE}

pbreg<-mcreg(log10(df$irf_percent_chop),(df$IRF_hup), method.reg = "WDeming",na.rm = TRUE)

b0<-pbreg@glob.coef[1] %>% round(3)
b1<-pbreg@glob.coef[2] %>% round(3)
estim<- pbreg@para

LCI.I<-estim[1,3] %>% round(3)
UCI.I<-estim[1,4] %>% round(3)
LCI.S<-estim[2,3] %>% round(3)
UCI.S<-estim[2,4] %>% round(3)

pcro<-cor(log10(df$irf_percent_chop),(df$IRF_hup),use = "complete.obs",method = "pearson") %>% round(3)


```


```{r, eval=FALSE}
plot(pbreg,  x.lab = "Log Sysmex XN", y.lab = "BC DxH")

# sctest(log10(df$irf_percent_chop)~df$IRF_hup)

```

Using the model to generate an "adjusted" IRF for the XN, below would be the correlation plot and the bias plots.

```{r, eval=FALSE}
df<-df %>% 
  mutate(d_irf = log10(irf_percent_chop)*b1+b0) %>% 
  rowwise() %>% 
  mutate(avg_d = sum(IRF_hup,d_irf)/2,
         delta_d = IRF_hup - d_irf,
         delta_p_d = delta_d/avg_d)

avg_delta_d<-mean(df$delta_d,na.rm = T)
avg_delta_p_d<-mean(df$delta_p_d,na.rm = T)

ggplot(df,aes(d_irf,IRF_hup))+
  geom_point()+
  geom_smooth()+
  labs(x="Adjusted IRF Sysmex XN",y="IRF BC DxH")
```

```{r, eval=FALSE}
ggplot(df,aes(avg_d,delta_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="DxH - XN")

ggplot(df,aes(avg_d,delta_p_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Avergage IRF",
       y="Percent difference")
  
```
