---
title: "Mindray 860/Sysmex XN IRF Correlation"
author: "Amrom"
date: "2018-09-06"
output: workflowr::wflow_html
---

## Analyzers

- Sysmex XN
- Mindray 8600


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#library(here,lib.loc = "~/icsh_rf/library")
#source(here::here("functions","funs.R"))
source("~/icsh_irf/functions/funs.R")
load_libs()
```

## Data

```{r}
mydata<-read_xlsx(here("data","spain.xlsx"),sheet = 2,range = "A2:I372")
```



```{r}
colnames(mydata)<-mydata %>%
  clean_names() %>% 
  colnames() %>% 
  paste0("_XX") %>% 
  str_replace_all(pattern = "1_XX","mind") %>% 
  str_replace_all(pattern = "XX","xn")

mydata <- mydata %>% 
  tidyr::fill(x_mind,.direction="down") %>% 
  filter(!str_detect(irf_xn,"nalyz")) %>% 
  mutate_at(2:9,as.numeric) 

```


```{r}
mydf <- mydata %>% 
  group_by(x_mind) %>% 
  summarise_all(mean)

number_rows<-nrow(mydf)
```

There are `r number_rows` comparisons in the data set, each performed in triplicate.

The following figure depicts the distribution of each of the parameters measured.

```{r}
gg<- mydf %>% 
  gather(key = "param",value = "value",-x_mind)
ggplot(gg,aes(value))+
  geom_histogram()+
  facet_wrap(~param,scales = "free",nrow = 2,dir = "v")
```

## Plots

Data was visualized with dot plots overlayed with loess smooth curve (blue) and a linear model (green). Since the linear model approximated the data well, a Deming regression was pursued on untransformed data.


```{r}

firstgg(mydf$irf_xn,mydf$irf_mind)+
  labs(x="IRF Sysmex XN",y="IRF Mindray")



```


## Bias Plots
```{r}

xx<-biaser(mydf$irf_xn,mydf$irf_mind)
xx[[1]]<-xx[[1]]+labs(y="XN - Mindray")

plot_grid(xx[[1]],xx[[2]])

```



## Deming regression

A Deming regression model was fitted. 

```{r, results='markup'}

dems<-mydems(mydf$irf_xn,mydf$irf_mind)

plot(dems[[1]],  x.lab = "Sysmex XN", y.lab = "Mindray")

```


Using the model to generate an "adjusted" IRF for the XN, below would be the correlation plot and the bias plots.

```{r}
df<-mydf %>% 
  mutate(d_irf =  irf_xn * dems[[3]] + dems[[2]]) %>% 
  rowwise() %>% 
  mutate(avg_d = sum(irf_mind,d_irf)/2,
         delta_d = irf_mind - d_irf,
         delta_p_d = delta_d/d_irf)

avg_delta_d<-mean(df$delta_d,na.rm = T)
avg_delta_p_d<-mean(df$delta_p_d,na.rm = T)

ggplot(df,aes(d_irf,irf_mind))+
  geom_point()+
  labs(x="Adjusted IRF Sysmex XN",y="IRF Mindray")
```

```{r}


p1<-ggplot(df,aes(avg_d,delta_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Mindray - XN")

p2<-ggplot(df,aes(avg_d,delta_p_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Percent difference")


plot_grid(p1,p2)

  
```

```{r}
qqnorm(df$delta_d)
```

