---
title: "Abbot Sapphire/Sysmex XN IRF Correlation"
author: "Amrom"
date: "2018-09-09"
output: workflowr::wflow_html
---

## Analyzers

- Sysmex XN
- Abbott Sapphire


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#library(here,lib.loc = "~/icsh_rf/library")
#source(here::here("functions","funs.R"))
source("~/icsh_irf/functions/funs.R")
load_libs()
```

## Data

```{r}
mydata<-read_xlsx(here("data","IRF Data Collection Instrument-DAUH.xlsx"),sheet = 2,range = "A2:I408")
```



```{r}
colnames(mydata)<-mydata %>%
  clean_names() %>% 
  colnames() %>% 
  paste0("_XX") %>% 
  str_replace_all(pattern = "1_XX","sapphire") %>% 
  str_replace_all(pattern = "XX","xn")

mydata <- mydata %>% 
  tidyr::fill(x_sapphire,.direction="down") %>% 
  filter(!str_detect(irf_xn,"nalyz")) %>% 
  mutate_at(2:9,as.numeric) 

```


```{r}
mydf <- mydata %>% 
  group_by(x_sapphire) %>% 
  summarise_all(mean)

number_rows<-nrow(mydf)
```

There are `r number_rows` comparisons in the data set, each performed in triplicate.

The following figure depicts the distribution of each of the parameters measured.

```{r}
gg<- mydf %>% 
  gather(key = "param",value = "value",-x_sapphire)
ggplot(gg,aes(value))+
  geom_histogram()+
  facet_wrap(~param,scales = "free",nrow = 2,dir = "v")
```

## Plots

Data was visualized with dot plots overlayed with loess smooth curve (blue) and a linear model (green). Since the linear model approximated the data well, a Passing-Bablok regression was pursued on untransformed data.


```{r}
ggplot(mydf,aes(irf_xn,irf_sapphire))+geom_point()
firstgg(mydf$irf_xn,mydf$irf_sapphire)+
    labs(x="IRF Sysmex XN",y="IRF Sapphire")
```


## Bias Plots
```{r}

xx<-biaser(mydf$irf_xn,mydf$irf_sapphire)
xx[[1]]<-xx[[1]]+labs(y="XN - Sapphire")

plot_grid(xx[[1]],xx[[2]])

```



## Passing-Bablok regression

A Passing-Bablok regression model was fitted using the log transformed XN IRF data and the raw DxH data. 

```{r, results='markup'}

dems<-mydems(mydf$irf_xn,mydf$irf_sapphire)

plot(dems[[1]],  x.lab = "Sysmex XN", y.lab = "Sapphire")

```


Using the model to generate an "adjusted" IRF for the XN, below would be the correlation plot and the bias plots.

```{r}
df<-mydf %>% 
  mutate(d_irf =  irf_xn * dems[[3]] + dems[[2]]) %>% 
  rowwise() %>% 
  mutate(avg_d = sum(irf_sapphire,d_irf)/2,
         delta_d = irf_sapphire - d_irf,
         delta_p_d = delta_d/d_irf)

avg_delta_d<-mean(df$delta_d,na.rm = T)
avg_delta_p_d<-mean(df$delta_p_d,na.rm = T)

ggplot(df,aes(d_irf,irf_sapphire))+
  geom_point()+
  labs(x="Adjusted IRF Sysmex XN",y="IRF Sapphire")
```

```{r}


p1<-ggplot(df,aes(avg_d,delta_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Sapphire - XN")

p2<-ggplot(df,aes(avg_d,delta_p_d))+
  geom_point()+
  geom_hline(yintercept = avg_delta_p_d)+
    geom_hline(yintercept = 0, linetype=2)+
  labs(x="Fitted Value",
       y="Percent difference")


plot_grid(p1,p2)

  
```

```{r}
qqnorm(df$delta_d)
```

```{r}

cv_result <- df %>% 
  filter(irf_xn>0) %>% 
  filter(d_irf>0) %>% 
  filter(irf_sapphire>0) %>% 
  mutate(log_irf_xn = log(irf_xn),
         log_d_irf = (log(d_irf)),
         log_irf_sapphire = (log(irf_sapphire))) %>% 
  rowwise() %>% 
  mutate(log_new = ((log_d_irf-log_irf_sapphire)^2)/2,
         log_old = ((log_irf_xn-log_irf_sapphire)^2)/2) %>% 
  ungroup %>% 
  summarise(cv_new = exp(sqrt(mean(log_new,na.rm = TRUE)))-1,
            cv_old = exp(sqrt(mean(log_old,na.rm = TRUE)))-1)

# df %>% 
#   rowwise() %>% 
#   mutate(delta_old =irf_xn - irf_sapphire,
#          delta_new = d_irf - irf_sapphire) %>% 
#   mutate(mean_old = (irf_xn + irf_sapphire)/2,
#          mean_new = (d_irf + irf_sapphire)/2) %>% 
#   ungroup %>% 
#   mutate(squ_old = (delta_old/mean_old)^2,
#          squ_new = (delta_new/mean_new)^2) %>% 
#   ungroup %>% 
#   filter(squ_new<10) %>% 
#   summarise(cv_old = sqrt(mean(squ_old,na.rm = TRUE)),
#             cv_new = sqrt(mean(squ_new,na.rm = TRUE)))



```

## Simulated Harmonization

We next calculated the the coefficient of variation between measures of IRF from the instruments and after simulated harmonization. Simulated harmonization means using the results of the Passing-Bablok regression to predict how a calibration procedure would alter the results. These simultated results are then used to calculate a predicted coefficient of variation after a calibration procedure.

Using the original IRF data, the CV between the methods is `r cv_result$cv_old`. After adjust the data using the regression equation, the CV reduces to `r cv_result$cv_new`. 

